DOpElib: A Goal Oriented Software Library for Computing PDEs and Optimization Problems

### 2012-10-22 Paper_May_2012/main.tex
Kleines Update of DWR-Beispiel

\subsection{Goal-oriented mesh refinement for Navier-Stokes}
Christian.

>>>>

\subsection{Goal-oriented mesh refinement for Navier-Stokes}
Christian.
In this example we consider a laminar flow around a cylinder in 2d. To be more precise, we are computing the benchmark 2D-1 from \cite{TuSchae96}. The computational domain is as depicted in figure~\ref{fig:example_ns}. We want to compute the drag force on the enclosed cylinder
\begin{equation}
c_D = \frac 1 {20} \int_{\Gamma_{circ}} \nu\partial_nu _1 - pn,
\end{equation}
with the normal $n$ and $\nu = 0.001$. To achieve an efficient computation of the quantity $c_D$, we employ goal-oriented mesh refinement with the help of the DWR-method, see \cite{BeRa96}.

\begin{itemize}
\item Bild Freiheitsgrade vs Fehler, global und 
\item Bild adaptive mesh, bild der Loesung (?)
\item eventuell kurz auf duale gleichung eingehen.
\end{itemize}
